ANGSD-wrapper: utilities for analyzing next generation sequencing data

### 2016-01-29 manuscript.tex
Changed some stuff stylistically

Here we present ANGSD-wrapper, a user-friendly interface to stable versions of ANGSD. 
ANGSD-wrapper takes the form of a set of configuration files and `wrapper' scripts (Figure \ref{fig:supp2}) that streamline the execution of multi-step pipelines required for data analysis in ANGSD. 
ANGSD-wrapper also eases the configuration of ANGSD-related programs such as \tjyk{Fumagali citation doesn't show up properly}ngsPopGen \citep{ngsPopGen}, ngsF\citep{vieira2013estimating}, and ngsAdmix \citep{pmid24026093}. 
\ph{This could be reworded} Furthermore, ANGSD-wrapper allows for easy population genetic analysis across the sequence data provided, or hone in on a certain region or subset of regions, allowing a highly-tailored experience.
Additionally, the wrapper scripts are written against ``frozen'' versions of ANGSD and supporting tools, for consistency of analysis. 
Because the large volume of data associated with high throughput sequence analysis is often difficult to visualize, ANGSD-wrapper also provides a suite of interactive visualization tools to plot results and explore patterns at multiple scales.  
We demonstrate some of the analyses possible using ANGSD-wrapper when applied to low-coverage whole-genome data from domesticated maize and two related wild teosinte subspecies. 
ANGSD-wrapper is freely available from \url{https://github.com/mojaveazure/angsd-wrapper}.

\section*{Methods}
\ph{change of language} ANGSD-wrapper is a set of configuration files and scripts written primarily in the Bash scripting language. %UNIX shell.  
The scripts can be run either on a standalone computer with a UNIX terminal, \ph{has anyone tested AW on a cluster?} or on computing clusters where they can be submitted to a queuing system such as SGE \citep{Microsystems):2001:SGE:560889.792378}, Slurm \citep{Jette02slurm:simple} or TORQUE \citep{Staples:2006:TRM:1188455.1188464}.  
A Python installation \citep{Python} is required for some light, dynamic pre-processing of the data.
An installation of the statistical software R \citep{Rcitation} is required to make use of the visualization tools incorporated in ANGSD-wrapper.  
The visualization portion of ANGSD-wrapper also requires installation of the R packages \texttt{Shiny} \citep{shiny}, \texttt{APE} \citep{APE}, \texttt{Lattice} \citep{lattice}, \texttt{Hmisc} \citep{Hmisc}, \texttt{data.table} \citep{datatable}, \texttt{DT} \citep{javascriptDT}, and \texttt{shinythemes} \citep{shinythemes}, as well as \texttt{genomeIntervals} \citep{genomeIntervals} from Bioconductor \citep{bioconductor} for the visualization package.
These dependent packages are installed automatically upon first run of visualization interface.

>>>>

Here we present ANGSD-wrapper, a user-friendly interface to stable versions of ANGSD. 
ANGSD-wrapper takes the form of a set of configuration files and `wrapper' scripts (Figure \ref{fig:supp2}) that streamline the execution of multi-step pipelines required for data analysis in ANGSD. 
ANGSD-wrapper also eases the configuration of ANGSD-related programs such as \tjyk{Fumagali citation doesn't show up properly}\ph{I think the citation is just 'Fumagali' and the link to the webpage. If so, then it works for me -PH}ngsPopGen \citep{ngsPopGen}, ngsF\citep{vieira2013estimating}, and ngsAdmix \citep{pmid24026093}. 
\ph{This could be reworded} Furthermore, ANGSD-wrapper allows for easy population genetic analysis across the sequence data provided, or hone in on a certain region or subset of regions, allowing a highly-tailored experience.
Additionally, the wrapper scripts are written against `frozen' versions of ANGSD and supporting tools, for consistency of analysis. 
Because the large volume of data associated with high throughput sequence analysis is often difficult to visualize, ANGSD-wrapper also provides a suite of interactive visualization tools to plot results and explore patterns at multiple scales.  
We demonstrate some of the analyses possible using ANGSD-wrapper when applied to low-coverage whole-genome data from domesticated maize and two related wild teosinte subspecies. 
ANGSD-wrapper is freely available from \url{https://github.com/mojaveazure/angsd-wrapper}.

\section*{Methods}
ANGSD-wrapper is a set of configuration files and scripts written primarily in the Bash scripting language. 
The scripts can be run either on a standalone computer with a UNIX terminal, \ph{has anyone tested AW on a cluster?} or on computing clusters where they can be submitted to a queuing system such as SGE \citep{Microsystems):2001:SGE:560889.792378}, Slurm \citep{Jette02slurm:simple} or TORQUE \citep{Staples:2006:TRM:1188455.1188464}.  
A Python installation \citep{Python} is required for some light, dynamic pre-processing of the data.
An installation of the statistical software R \citep{Rcitation} is required to make use of the visualization tools incorporated in ANGSD-wrapper.  
The visualization portion of ANGSD-wrapper also requires installation of the R packages \texttt{Shiny} \citep{shiny}, \texttt{APE} \citep{APE}, \texttt{Lattice} \citep{lattice}, \texttt{Hmisc} \citep{Hmisc}, \texttt{data.table} \citep{datatable}, \texttt{DT} \citep{javascriptDT}, and \texttt{shinythemes} \citep{shinythemes}, as well as \texttt{genomeIntervals} \citep{genomeIntervals} from Bioconductor \citep{bioconductor} for the visualization package.
These dependent packages are installed automatically upon first run of visualization interface.
